%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemWithoutTitle}[1]{
    \item\small{
            {\vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Marsel Akhmetov}} & Email : \href{mailto:marsel.ahmetov974@gmail.com}{marsel.ahmetov974@gmail.com}\\
\href{https://www.linkedin.com/in/marsel-akhmetov/}{Linkedin: https://www.linkedin.com/in/marsel-akhmetov/} & Mobile : +7-900-628-33-27 \\
\href{https://github.com/mokaruuns}{Github: https://github.com/mokaruuns} \\
\href{https://github.com/mokaruuns}{Telegram: https://t.me/mokaruuns} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{VK, MyTracker}{Saint-Petersburg, Russia}
{Junior fullstack developer}{March 2022 - Current}
\resumeItemListStart
\resumeItem{Enhancement of Infrastructure Monitoring Service}
{Significantly contributed to enhancing our internal monitoring tool by adding new features that enriched data collection. This allowed management and decision-makers to more effectively gauge the need for server equipment purchases, facilitating timely and informed infrastructure upgrades.}
\resumeItem{Optimization of Birth Date Data Storage}
{Re-engineered the storage method for birth date information, greatly improving the accuracy of our user analytics. This led to more effective targeted marketing campaigns, enhancing user engagement and marketing ROI.}
\resumeItem{Contribution to E-Commerce API Development}{Played a crucial role in the development of a s2s-api for e-commerce platforms, contributing to better data integration. This initiative provided valuable insights for marketing optimization and supported more efficient, data-driven decision-making.}
\resumeItem{Development of a Weekly Report Generation Service}{Created a service for generating weekly reports on team members' tasks, aimed at improving the monitoring of team performance. This tool has been instrumental in increasing transparency and accountability within the team, leading to enhanced productivity and project management efficiency.}
\resumeItemListEnd
{In my role at MyTracker, my focus was on backend development, which included enhancing data processing workflows, integrating with partners, and developing robust APIs. My work primarily involved PHP and MySQL, and I also expanded my skills with NoSQL and columnar databases, contributing significantly to the efficiency and capability of our analytics platform.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{ITMO University}{St. Petersburg, Russia}
{Bachelor of Science in Computer Science}{Sep 2020 - current}

{\scriptsize \textit{
Courses:
Operating Systems,
Data Structures and Algorithms,
Web Development,
Database Fundamentals,
Software Engineering
}}
\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Hardware skills}{Python, FastAPI, AsyncIO, Celery, PHP, Symfony, PostgreSQL, GitFlow, Docker, GraphQL, React }
\resumeSubItem{Soft skills}{rapid project adaptation, product responsibility, teamwork}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{VK Bot on PHP} {PHP, Python, VK API, PostgreSQL, Docker, Linux, Nginx}
{\href{https://github.com/mokaruuns/bot-recipes}{https://github.com/mokaruuns/bot-recipes}}{Dec 2022}
\resumeItemListStart
\resumeItem{Data Retrieval}{Utilize Python and BeautifulSoup to parse a website and extract all recipes.}
\resumeItem{Database Design}{Architect the database using PostgreSQL to efficiently store recipes and user data. Establish tables and relationships for rapid and convenient data access.}
\resumeItem{Software Development}{Create a bot with PHP and VK API that can deliver recipes to users based on various parameters.}
\resumeItem{Deployment}{Deploy the bot on a server using Docker and Nginx.}
\resumeItemListEnd

\resumeSubheading
{Regex parser} {Java, Graphviz}
{\href{https://github.com/mokaruuns/parsing/tree/main/recursive-parsing}{https://github.com/mokaruuns/parsing/tree/main/recursive-parsing}}{Sep 2022}
\resumeItemListStart
\resumeItem{Grammar Creation}{Develop an LL(1) grammar for regular expressions.}
\resumeItem{Implementation}{Create a regular expression parser in Java based on the grammar.}
\resumeItem{Unit Testing}{Test the parser thoroughly with JUnit.}
\resumeItem{Visualization}{Automatically generate a graphviz diagram for expressions.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}[font=$\bullet$]
% \item {Selected in top 20 students for the Code House event organized by VMware in August15 - August17, 2016.}
% \item {Ranked first among batch of 60 students in my Computer Science Engineering Branch.}
% \item {Ranked fifth among batch of 500 students at High School Level A.I.S.S.E 2005}
% \end{description}
%-------------------------------------------

%-----------Summary-----------------
\section{Summary}
I'm Marsel Akhmetov, a results-driven Junior PHP Developer at VK with 1 year of experience and a 4th-year student at ITMO University. Specializing and aspiring to excel in backend development with a keen interest in advancing towards roles in SWE/SRE. Additionally, I am adept in Python, exploring Go. Eager to transition to Junior+/Middle Python/PHP Developer roles, I'm good at working with a team, take responsibility seriously, and can adapt to new projects quickly. I'm excited about joining innovative teams, always ready to learn, and committed to providing practical solutions. Thanks for considering my application.
\end{document}