%-------------------------
% Resume in Latex
% Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemWithoutTitle}[1]{
    \item\small{
            {\vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Marsel Akhmetov}} & Email : \href{mailto:marsel.ahmetov974@gmail.com}{marsel.ahmetov974@gmail.com}\\
\href{https://www.linkedin.com/in/marsel-akhmetov/}{Linkedin: https://www.linkedin.com/in/marsel-akhmetov/} & Mobile : +7-900-628-33-27 \\
\href{https://github.com/mokaruuns}{Github: https://github.com/mokaruuns} \\
\href{https://github.com/mokaruuns}{Telegram: https://t.me/mokaruuns} \\
\end{tabular*}

%-----------Summary-----------------
\section{Summary}
I am Marsel Akhmetov, a PHP/Go Developer with 2 years of experience at VK. I have completed my studies in Applied Mathematics and Computer Science from ITMO University.
Specializing in backend development, I am keen to excel in roles such as Software Engineer or Site Reliability Engineer. In addition to my expertise in PHP and Go, I am also adept in Python and continuously exploring new technologies.
I am looking for Middle Python/Go Developer roles, where I can leverage my skills and experience. I work well in teams, take responsibility seriously, and adapt quickly to new projects. I am committed to delivering practical solutions and am always eager to learn and grow.

%--------SKILLS------------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Programming Languages}{Go, Python, PHP, Java}
\resumeSubItem{Version Control}{Git, GitFlow}
\resumeSubItem{Containers and Deployment}{Docker, Kubernetes, Nginx, CI/CD}
\resumeSubItem{Databases}{MySQL, Clickhouse, Tarantool}
\resumeSubItem{API Development}{REST, GraphQL}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{ITMO University}{St. Petersburg, Russia}
{Bachelor of Science in Applied Mathematics and Computer Science}{Sep 2020 - Jun 2024}

{\scriptsize \textit{
Courses:
Operating Systems,
Data Structures and Algorithms,
Web Development,
Database Fundamentals,
Software Engineering
}}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{VK, MyTracker}{Saint-Petersburg, Russia}
{Junior Backend Developer}{March 2022 - Current}
\resumeItemListStart
\resumeItem{Enhancement of Infrastructure Monitoring Service with Jira Integration}
{Significantly improved the internal monitoring tool by adding new features, such as integration with Jira to track current hardware tasks and gather information about equipment. These enhancements enriched data collection, speeding up data analysis and budgeting, especially during incidents.}
\resumeItem{Contribution to E-Commerce API Development} {Added new methods to the s2s API for e-commerce, improving both the product and the public library for clients.}
\resumeItem{Development of Task Reporting and Management System}{Developed using PHP with Symfony, this system displays tasks and generates easy-to-read reports. It integrates with Jira to manage tasks and collect data, improving team performance monitori}
\resumeItem{VKTeams Bot for Duty Management}{Developed in Golang, this bot improves the duty shift process by managing and transferring task context. It has several features, including retrieving the current on-duty person, notifying the on-duty staff, and passing task information. This helps streamline communication and makes duty transitions smoother.}
\resumeItemListEnd
{At MyTracker, I focused on backend development. This included improving data processing, integrating with partners, and creating strong APIs. Additionally, I monitored continuous data collection for analytics and advertising during shifts, resolved incidents, added new features to ETL processes, and handled product tasks and analysis. I also led the migration from old hardware to a new Kubernetes environment.}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{VK Bot on PHP} {PHP, Python, VK API, PostgreSQL, Docker, Linux, Nginx}
{\href{https://github.com/mokaruuns/bot-recipes}{https://github.com/mokaruuns/bot-recipes}}{Dec 2022}
\resumeItemListStart
\resumeItem{Data Retrieval}{Utilize Python and BeautifulSoup to parse a website and extract all recipes.}
\resumeItem{Database Design}{Architect the database using PostgreSQL to efficiently store recipes and user data. Establish tables and relationships for rapid and convenient data access.}
\resumeItem{Software Development}{Create a bot with PHP and VK API that can deliver recipes to users based on various parameters.}
\resumeItem{Deployment}{Deploy the bot on a server using Docker and Nginx.}
\resumeItemListEnd

\resumeSubheading
{Regex parser} {Java, Graphviz}
{\href{https://github.com/mokaruuns/parsing/tree/main/recursive-parsing}{https://github.com/mokaruuns/parsing/tree/main/recursive-parsing}}{Sep 2022}
\resumeItemListStart
\resumeItem{Grammar Creation}{Develop an LL(1) grammar for regular expressions.}
\resumeItem{Implementation}{Create a regular expression parser in Java based on the grammar.}
\resumeItem{Unit Testing}{Test the parser thoroughly with JUnit.}
\resumeItem{Visualization}{Automatically generate a graphviz diagram for expressions.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}
